Verification of the CVM algorithm with a new Recursive Analysis Technique

### 2025-01-25 isabelle/CVM_Subsample/document/root.tex
Update root.tex
fix minor typo

In this entry, we verify the CVM algorithm's correctness using a new technique which simplifies
the formal analysis considerably compared to the orignal proof by Chakraborty et
al. The main idea is based on a probabilistic invariant that allows us to derive concentration using
Cram\'{e}r Chernoff method.

This new technique opens up the possible algorithm design space, and we introduce a new variant of the 
CVM algorithm, that is total, and also has an additional property in addition 
to concentration: unbiasedness. This means the expected result of the algorithm is exactly equal to
the desired result. The latter is also a new property, that neither the original CVM algorithm
nor classic algorithms for the distinct elements problem posses.
\end{abstract}

>>>>

In this entry, we verify the CVM algorithm's correctness using a new technique which simplifies
the formal analysis considerably compared to the orignal proof by Chakraborty et
al. The main idea is based on a probabilistic invariant that allows us to derive concentration bounds
using the Cram\'{e}r-Chernoff method.

This new technique opens up the possible algorithm design space, and we introduce a new variant of the
CVM algorithm, that is total, and also has an additional property in addition
to concentration: unbiasedness. This means the expected result of the algorithm is exactly equal to
the desired result. The latter is also a new property, that neither the original CVM algorithm
nor classic algorithms for the distinct elements problem possess.
\end{abstract}
